% !TEX program = pdflatex
% Short companion deck: AI agents for analog + digital block design.
% Sibling of tutorials/rtl2gds-gf180-docker/.
% Build:  make              -> main.pdf            (audience view)
%         make notes        -> main-with-notes.pdf (speaker view)

\documentclass[aspectratio=169,11pt]{beamer}
\input{preamble.tex}

\title{AI Agents for Analog and Digital IC Design}
\subtitle{What the eda-agents stack actually ships today}
\author{EDA-Agents Project}
\institute{Open-Source IC Design}
\date{\today}

\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

\begin{frame}{What you will learn}
  \begin{itemize}
    \item How the \cmd{eda-agents} repo splits AI assistance into two
          complementary loops: \term{analog} (sizing + SPICE) and
          \term{digital} (RTL-to-GDS).
    \item The roster of agents you can invoke today, and the infra
          they plug into (autoresearch, MCP, skills).
    \item Where to go to drive a real block end-to-end.
  \end{itemize}
  \vspace{0.4em}
  \textit{Sibling deck: \cmd{../rtl2gds-gf180-docker/} -- a hands-on
  LibreLane tutorial that uses the same Docker toolchain.}
  \note{%
    Orientation slide. This deck is intentionally short
    (~7 content frames) and schematic. Dense material lives in the
    \cmd{\textbackslash note\{...\}} blocks so an expert designer can
    import slides + notes into a polished deck with animations later.\par
    The main audience here is someone who has watched the RTL-to-GDS
    tutorial and is asking: ``can I automate the knob-turning?'' The
    answer this deck gives: yes, with two loops -- analog uses gm/ID
    sizing feedback from ngspice, digital uses LibreLane metrics --
    both wrapped in a topology-agnostic greedy search.}
\end{frame}

\begin{frame}{Agenda}
  \tableofcontents
\end{frame}

\input{sections/01-landscape.tex}
\input{sections/02-analog.tex}
\input{sections/03-digital.tex}
\input{sections/04-autoresearch.tex}
\input{sections/05-mcp.tex}
\input{sections/06-resources.tex}

\end{document}
