% !TEX program = pdflatex
% Tutorial: RTL-to-GDS with Docker + LibreLane + GF180MCU
% Audience: first-time users of open-source IC design flows
% Build:  make              -> main.pdf  (audience view, notes hidden)
%         make notes        -> main-with-notes.pdf  (speaker view)

\documentclass[aspectratio=169,11pt]{beamer}

\input{preamble.tex}

\title{RTL-to-GDS on GF180MCU}
\subtitle{LibreLane + Docker in practice}
\author{EDA-Agents Project}
\institute{Open-Source IC Design}
\date{\today}

\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

\begin{frame}{What you will learn}
  \begin{itemize}
    \item What RTL-to-GDS means end-to-end, and where LibreLane sits.
    \item How to get the full toolchain in \textbf{one Docker command}.
    \item How to configure LibreLane for a GF180MCU full-chip design
          (the config.yaml anatomy).
    \item How to run the flow and read DRC / LVS / timing signoff.
  \end{itemize}
  \vspace{0.5em}
  \textbf{Prerequisites:} Linux host, Docker installed, $\sim$40\,GB free disk.
  \textit{No prior EDA knowledge assumed.}
  \note{%
    Reset expectations. This deck is compressed on purpose: background on
    Docker, open-source philosophy, and tool internals is pushed to the
    notes or external links. The slides chase the shortest path to
    ``LibreLane runs and produces a green chip.''\par
    A companion Jupyter notebook
    (\cmd{tutorials/rtl2gds-gf180-docker/demo/rtl2gds\_counter.ipynb}) ships
    a 4-bit counter through LibreLane in 8 cells. Use that for hands-on
    iteration after this talk.}
\end{frame}

\begin{frame}{Agenda}
  \tableofcontents
\end{frame}

\input{sections/01-pipeline.tex}
\input{sections/02-stack-pdk-container.tex}
\input{sections/03-librelane-config.tex}
\input{sections/04-run-the-flow.tex}
\input{sections/05-flow-stages.tex}
\input{sections/06-results-pitfalls-next.tex}

\end{document}
