\section{Where to go next}

\begin{frame}{Starting points}
  \begin{itemize}\small
    \item \textbf{Run the analog loop:}
          \cmd{examples/07\_autoresearch\_circuit.py} -- Miller OTA
          sizing with SPICE feedback.
    \item \textbf{Run the digital loop:}
          \cmd{examples/09\_rtl2gds\_digital.py --backend cc\_cli}
          drives the 5-agent tree end-to-end on GF180 or IHP.
    \item \textbf{Tune LibreLane knobs:}
          \cmd{examples/10\_digital\_autoresearch.py} (greedy search).
    \item \textbf{Claude Code agent invocations:}
          \cmd{/agents gf180-docker-digital},
          \cmd{/agents analog-sizing-advisor},
          \cmd{/agents analog-topology-recommender}.
    \item \textbf{Hands-on tutorial:}
          \cmd{../rtl2gds-gf180-docker/demo/rtl2gds\_counter.ipynb} --
          4-bit counter, 8 notebook cells.
  \end{itemize}
  \vspace{0.6em}
  \footnotesize
  Source of truth for names + tool rosters:
  \cmd{.claude/agents/*.md}, \cmd{src/eda\_agents/agents/digital\_adk\_agents.py},
  \cmd{src/eda\_agents/skills/\{analog,digital\}.py}.
  \note{%
    Starter recipe for a new user: run the analog example first (it's
    fast, under 5 min on a laptop, and teaches the
    \cmd{program.md} / \cmd{results.tsv} convention); then try
    \cmd{09\_rtl2gds\_digital.py --dry-run} to see the agent flow
    without spending LLM tokens; then the counter notebook.\par
    For real work: invoke the Claude Code agent slash commands.
    \cmd{/agents gf180-docker-digital} hands you a Claude Code session
    with the toolchain, skills, and safety rails already wired in.
    Safer than copy-pasting prompts.}
\end{frame}

\begin{frame}{Thank you}
  \begin{center}
    \Large The agents are infrastructure, not magic.\\[0.4em]
    \normalsize Every tool they use is in the repo. Read the code.\\[0.8em]
    \small \cmd{github.com/Mauricio-xx/eda-agents}
  \end{center}
  \note{%
    Closing stance: resist the framing that ``AI does the design.''
    What actually happens is that humans encoded a design methodology
    (gm/ID for analog, the LibreLane flow for digital) as skills,
    topologies, and evaluators; the LLM drives the loop, but the loop
    is made of our code and our rules. Debugging an autoresearch run is
    reading \cmd{program.md} and \cmd{results.tsv}, not prompting
    harder.\par
    Invite questions on: adding a new topology, adding a new skill,
    wiring a new PDK, or integrating a custom evaluator.}
\end{frame}
